

### InDel Statistics and Annotation
&emsp;&emsp;InDel refers to small fragment insertions and deletions in the genome.The LASTZ (Version 1.03.54) software was used to detect small fragment insertions and deletions (InDel) with lengths less than 50bp. The types of InDel were statistically analyzed, and the results are shown in the following table:

<p class='mark'>Table<font face="Arial">2-22 Statistics of InDel Types</p>

```{r echo=FALSE}
library(DT)
data <- read.delim('file/06.Comparative_Genomics/indel.xls',sep='\t',header=T)
datatable(data,rownames=FALSE,extensions=c('KeyTable','Buttons','FixedColumns'),options=list(keys=T,scrollX=T,dom = 'Bfrtip',buttons = list('copy', 'print', list(extend = 'collection',buttons = c('csv', 'excel', 'pdf'),text = 'Download')),initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color':'#4682B4','color': 'white'});","}")),class='nowrap')
```

- **<font face="Arial">Reference Name</font>**：Reference sequence ID
- **<font face="Arial">Sample ID</font>**：Sample ID
- **<font face="Arial">Frame-shifted</font>**：ORF frameshift mutation
- **<font face="Arial">Start codon</font>**：ORF start codon disrupted
- **<font face="Arial">Stop codon</font>**：ORF stop codon disrupted
- **<font face="Arial">Premature stop</font>**：ORF terminated prematurely
- **<font face="Arial">Effect</font>**：No significant impact on ORF
- **<font face="Arial">CDS with indel</font>**：Number of CDS containing InDels
- **<font face="Arial">All CDS</font>**：Total number of CDS in the reference sequence


&emsp;&emsp;Annotation of the InDels was performed, and the annotation results are presented in the table below:
<p class='mark'>Table<font face="Arial">2-20 InDel Annotation Statistics</p>

```{r echo=FALSE}
library(DT)
data <- read.delim('file/06.Comparative_Genomics/indel_anno.xls',sep='\t',header=T)
datatable(data,rownames=FALSE,extensions=c('KeyTable','Buttons','FixedColumns'),options=list(keys=T,scrollX=T,dom = 'Bfrtip',buttons = list('copy', 'print', list(extend = 'collection',buttons = c('csv', 'excel', 'pdf'),text = 'Download')),initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color':'#4682B4','color': 'white'});","}")),class='nowrap')
```

- **<font face="Arial">Reference Name</font>**：Reference sequence ID
- **<font face="Arial">Sample ID</font>**:Sample ID
- **<font face="Arial">Start codon ins</font>**：Insertion located at the start codon
- **<font face="Arial">CDS inside ins</font>**：Insertion located within the CDS
- **<font face="Arial">Stop codon ins</font>**：Insertion located at the stop codon
- **<font face="Arial">Start codon del</font>**：Deletion located at the start codon
- **<font face="Arial">CDS inside del</font>**：Deletion located within the CDS
- **<font face="Arial">Stop codon del</font>**：Deletion located at the stop codon


&emsp;&emsp;Result directory：Result/06.Comparative_Genomics/InDel/

